% vim: set tw=160:

\chapter{Workers who use a computer earn roughly 10-15 percent higher pay, other things being equal.}

\section{What does “other things being equal” mean? }
Other things being equal means that if you have to people who are completely identical except one works with a computer earns 10-15 percent more than the other person without a computer at work.
In this case, this means that people with the same education, same working experience, sex, race, etc.

\section{Why is it important to hold other things equal?}
It is so important because it is only one thing measured without interdependencies. If you hold everything equal except one thing, we are just measuring the impact of this thing.
Withholding thing equal we can determine causation. In this example, we can say that workers who use computers earn more because other things are held equal. If this wouldn't be the case, we couldn't be sure if we measure interdependencies or the impact of something else.

\section{How does the paper reach its conclusion step by step?}
It starts with descriptive analysis and a table of workers who directly use a computer at work. Then the computer use and wages are analyzed and a regression table of the estimated effect of computer use on pay was created. Then external inputs were measured like the employee characteristic. What is more, the computer premium over time and the specific computer task was analyzed with a table of the return to various uses of computers. The next chapter was about if the differential of computer wages is real or illusion. Therefore different characteristics where measured. Like the use of a computer at home and at work. With the return to computer use at work, home, and work and home a table was created. In this table, the characteristics confronted between the year 1984 and 1989. After this, a table with wage regression estimates for secretaries was presented. There were secretaries compared in 1984 and 1989. Next,  the High School and Beyond Survey were taken to show the regression wage regression of students from high school. This table also showed that people who were using computers earned more. In the following, more tables were presented like the regression estimates of the effect of computer use on pay and the effect of computer use on the return to education. After this, an equation was prepared. The equation shows the dependent variable wage and the independent variables which affect the wage. The independent variables are education, computer-use, and covariates. 

